---
title: "Logistical Regression"
author: "Dee Muralidharan"
date: "August 17, 2017"
output: html_document
---
## Exercise: logistic regression
## ───────────────────────────────────

##   Use the NH11 data set that we loaded earlier.

##   1. Use glm to conduct a logistic regression to predict ever worked
##      (everwrk) using age (age_p) and marital status (r_maritl).
##   2. Predict the probability of working for each level of marital
##      status.

##   Note that the data is not perfectly clean and ready to be modeled. You
##   will need to clean up at least some of the variables before fitting
##   the model.

```{r setup, include=FALSE}

setwd ("D:/springboard Data science/Exercises/Linear Regression 2")
NH11 <- readRDS("D:/springboard Data science/Exercises/Linear Regression 2/NatHealth2011.rds")
str(NH11)
levels(NH11$hypev)
hyp.out <- glm (everwrk~ age_p + r_maritl, data = NH11,  family = "binomial")
summary(hyp.out)
```

##   2. Predict the probability of working for each level of marital

##      status.

```{r}
library(effects)
plot(allEffects(hyp.out))
```

